\documentclass[]{article}

\begin{document}
\begin{center}
\Large Exam 1: Study guide
\end{center}

Exam 1 for CE 311K is a one-hour closed-book exam held on 10th October 2019 in JGB 2.218 during class time. You may bring one sheet of 8.5 x 11 inch of your own handwritten notes to the examination. You may use your calculator. You may not access the internet during the exam. The exam questions will be determined such that they satisfy a subset of the objectives listed here.

Exam 1 will cover:
\begin{itemize}
	\item Lecture handouts \# 1, \#2 and pages 16 - 18 in \# 3 Errors (absolute and relative errors)
	\item Homeworks 1 and 2 (Variables, Iterations and Control flow)
	\item Labs 00 through 01c (Variables, Iterations and Control flow, nested loops and plots)
\end{itemize}

To perform successfully on Exam I, you should be able to:

\begin{enumerate}
	\item Determine data types (\verb|bool|, \verb|int|, \verb|float|, \verb|string|) of different operations (for e.g, $*, +, -, /, \%, //$)
	\item Write simple programs using variables and evaluate the value bound to a variable(s) at different step(s) in the code.
	\item Understand and evaluate the order of precedence in a given statement(s).
	\item Identify syntax, semantic and static-semantic errors in the code. It is not required to identify the exact type of error in the code, but the location of an error(s) in the code.
	\item Identify and fix incorrect code either using the output error message, verification result or logic.
	\item Understand and develop logic / algorithms / code that involve iterations (single and nested \verb|for|, \verb|for - else| and \verb|range|) and control flow (\verb|if|, \verb|elif|, \verb|else|, \verb|break| and \verb|continue|).
	\item Understand the output of a given code or expression (for e.g., \verb|range()|)
	\item Explain in your own word what are relative and absolute errors.
	\item Evaluate relative and absolute erorr(s) for a given program. 
	\item Evaluate a suitable termination criteria (\verb|break|) based on the relative or absolute error.


\end{enumerate}

You won't be required to write lengthy code (more than 30 lines). I will not penalise for obvious typos and syntax errors in your code (for e.g., missing \verb|:| at the end of control flow statements), unless that is what is tested.
\end{document}
